Psychological Needs During Intergroup Contact

### 2021-11-05 Tables/studentVarDescr.tex
AOT-M Methods first draft
AOT-M contact hypothesis code added

\caption{Student: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llcccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
\midrule
Core Need &  & 0.65*** & 0.67*** & 0.28** & 0.27**\\
Competence & 0.30*** &  & 0.66*** & 0.59*** & 0.08\\
Autonomy & 0.18*** & 0.33*** &  & 0.43*** & -0.08\\
Relatedness & 0.43*** & 0.21*** & 0.12*** &  & -0.13\\
Attitudes NL & 0.17*** & 0.08*** & 0.08*** & 0.08*** & \\
\addlinespace
Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 67.26\\
Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 18.64\\
Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 9.40\\
ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.80\\
ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.99\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{minipage}
\end{table}

>>>>

\caption{\label{tab:studentVarDescr}Student: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.60*** & 0.66*** & 0.43*** & 0.78*** & 0.11\\
Competence & 0.24*** &  & 0.71*** & 0.65*** & 0.74*** & 0.09\\
Autonomy & 0.15*** & 0.34*** &  & 0.56*** & 0.67*** & -0.06\\
Relatedness & 0.45*** & 0.29*** & 0.42*** &  & 0.54*** & -0.11\\
Quality & 0.17*** & 0.39*** & 0.08*** & 0.05** &  & 0.10\\
Attitudes NL & 0.35*** & 0.43*** & 0.11*** & 0.10*** & 0.12*** & \\
\addlinespace
Grand Mean & 84.87 & 72.55 & 82.59 & 61.21 & 83.77 & 67.26\\
Between-person SD & 9.17 & 14.47 & 11.21 & 13.36 & 9.12 & 18.64\\
Within-person SD & 20.33 & 21.17 & 16.06 & 28.74 & 16.80 & 9.40\\
ICC(1) & 0.15 & 0.30 & 0.32 & 0.17 & 0.20 & 0.80\\
ICC(2) & 0.89 & 0.95 & 0.95 & 0.90 & 0.88 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{minipage}
\end{table}

### 2021-11-05 Tables/workerVarDescr.tex
AOT-P methods added
effect size trials
AOT-M Methods first draft
AOT-M contact hypothesis code added

\begin{table}

\caption{\label{tab:workerSampleInfo}Worker: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llcccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Attitudes NL\\
\midrule
Core Need &  & 0.67*** & 0.54*** & 0.01 & -0.23\\
Competence & 0.36*** &  & 0.72*** & -0.14 & -0.20\\
Autonomy & 0.31*** & 0.09** &  & -0.05 & 0.19\\
Relatedness & 0.45*** & 0.09** & 0.14*** &  & -0.06\\
Attitudes NL & 0.05 & 0.11*** & 0.12*** & 0.14*** & \\
\addlinespace
Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 71.49\\
Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 12.91\\
Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 8.11\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.99\\
\bottomrule
\multicolumn{6}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{6}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{table}

>>>>

\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

\caption{\label{tab:workerVarDescr}Worker: Multilevel Core Variable Descriptives}
\centering
\begin{tabular}[t]{llccccc}
\toprule
  & Core Need & Competence & Autonomy & Relatedness & Quality & Attitudes NL\\
\midrule
Core Need &  & 0.82*** & 0.60*** & 0.33 & 0.52** & -0.03\\
Competence & 0.36*** &  & 0.89*** & 0.26 & 0.39 & -0.23\\
Autonomy & 0.28*** & 0.22*** &  & 0.31 & 0.57** & 0.02\\
Relatedness & 0.50*** & 0.39*** & 0.37*** &  & -0.07 & 0.14\\
Quality & 0.17*** & 0.44*** & 0.27*** & 0.26*** &  & 0.50*\\
Attitudes NL & 0.24*** & 0.36*** & 0.24*** & 0.37*** & 0.52*** & \\
\addlinespace
Grand Mean & 27.95 & 12.10 & 22.17 & 5.29 & 24.10 & 71.49\\
Between-person SD & 14.68 & 13.72 & 12.09 & 14.59 & 9.50 & 12.91\\
Within-person SD & 20.83 & 20.89 & 15.15 & 23.29 & 18.01 & 8.11\\
ICC(1) & 0.29 & 0.28 & 0.38 & 0.28 & 0.18 & 0.70\\
ICC(2) & 0.96 & 0.95 & 0.97 & 0.95 & 0.79 & 0.99\\
\bottomrule
\multicolumn{7}{l}{\rule{0pt}{1em}\textit{Note: }}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Upper triangle: Between-person correlations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}Lower triangle: Within-person coorelations;}\\
\multicolumn{7}{l}{\rule{0pt}{1em}*** p < .001, ** p < .01,  * p < .05}\\
\end{tabular}
\end{minipage}
\end{table}
